Increasing Productivity in the Domiciliary Care Sector Through Automated Routing and Scheduling of Carers

### 2021-05-25 tex/Pres180521/main.tex
new presentation for abicare using new dataset.

\begin{frame}{Task}
To create an efficient route and schedule for each carer such that all patients (jobs) are visited at the correct times by suitable carers.
\small
\begin{multicols}{2}
	\begin{itemize}
		\item Assign jobs to sufficiently skilled carer(s)
		\item Assign jobs to preferred carers(s)
		\item Assign carers to preferred jobs
		\item Workload balance %($\overline{B}$)
		\item Minimise waiting times %($\overline{W}$)
		\item Minimise tardiness %($\overline{Z}$)
		\item Minimise overtime %($\overline{O}$)
		\item Minimise travel time %($\overline{T}$)
		\item Minimise travel distance*
		%\item Assign jobs and carers according to preferences ($\overline{P}$)
	\end{itemize}	
\end{multicols}	
\end{frame}

@@

\begin{comment}
\begin{frame}{Queries}
\scriptsize
%\begin{multicols}{2}
	\begin{itemize}
		\item \note{Desired objective(s)}
		\item Are there skill ``levels'' for carers?
		\item Distinct job types or customised per job
		\item Jobs that \emph{cannot} start late
		\item Lunch breaks
		\item Parking availability at patient's home
		\item PPE/COVID-19 conditions
		\item Frequency of schedule formation
		\item Database/software currently used
		\item Hard and soft constraints
		\item Any additional constraints?
		\item Who will be using the application?
		\item Additional carers available?
	\end{itemize}	
%\end{multicols}
\end{frame}

@@

\end{frame}
\end{comment}

\begin{frame}{Comparison: Abicare vs DST}
\small
\begin{multicols}{3}	
\begin{block}{Hampshire}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 15
		\item Clients = 34
		\item Jobs = 480
	\end{itemize}
\end{block}
\begin{block}{Monmouth}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 23
		\item Clients = 47
		\item Jobs = 735
	\end{itemize}
\end{block}
\begin{block}{Aldershot}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 9
		\item Clients = 19
		\item Jobs = 184
	\end{itemize}
\end{block}
\end{multicols}	
\end{frame}

\begin{frame}{Comparison: Hampshire Time and Distance}
	\begin{figure}
		\includegraphics[width=0.5\linewidth]{figures/Hampshire_time_comparison_abi}%
		\includegraphics[width=0.5\linewidth]{figures/Hampshire_dist_comparison_abi}
	\end{figure}
\end{frame}

@@

\begin{comment}
\begin{frame}{Comparison}
	\begin{figure}[T]
		\includegraphics[width=0.5\linewidth]{figures/2_Nov_20_Hampshire_time_info_abi}%
		\includegraphics[width=0.5\linewidth]{figures/2_Nov_20_Hampshire_time_info_dst}
	\end{figure}
\end{frame}

>>>>

\begin{frame}{Queries}
	\scriptsize
	%\begin{multicols}{2}
	\begin{itemize}
		\item Size of the dataset provided
		\item Incomplete/incorrect postcodes (e.g. CU14 9DD, NP13)
		\item Travel to/from carer's homes to be included?
		\item Carers' locations between shifts (return home or elsewhere)
		\item Areas have multiple locations (e.g. AndoverSalisbury, AldershotHampshire)
		\item Clients' names in Carer Availability dataset
		\item Missing details for some clients/carers
		\item Duration of some tasks is 0 minutes
	\end{itemize}	
	%\end{multicols}
\end{frame}

\begin{frame}{Clients' Names in Carer Availability Dataset}
	\begin{figure}
		\includegraphics[width=1\linewidth]{figures/ClientNames}%
	\end{figure}
\end{frame}

\begin{frame}{Incorrect Postcodes and Multiple Locations}
\begin{columns}
	\column{0.5\textwidth}
	\begin{minipage}[c][1\textheight][c]{\linewidth}
		\includegraphics[width=1\linewidth]{figures/IncorrectPostcodes}
	\end{minipage}
	\column{0.5\textwidth}
	\begin{minipage}[c][1\textheight][c]{\linewidth}
		\includegraphics[width=0.8\linewidth]{figures/MultipleAreas}
	\end{minipage}
\end{columns}
\end{frame}

\begin{frame}{Comparison: Salisbury vs Hampshire}
	\small
	\begin{multicols}{2}	
		\begin{block}{Salisbury}
			\begin{itemize}
%				\setlength{\itemindent}{-.1in}
				\item Carers = 35
				\item Shifts = 70
				\item Jobs = 14
			\end{itemize}
		\end{block}
		\begin{block}{Hampshire}
			\begin{itemize}
%				\setlength{\itemindent}{-.1in}
				\item Carers = 21
				\item Shifts = 24
				\item Jobs = 68
			\end{itemize}
		\end{block}
	\end{multicols}	
\end{frame}

% Salisbury original vs including nursesto/from home. nNurses = 35, nJobs = 14, nShifts = 70
\begin{frame} 
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\textbf{Salisbury}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.7\linewidth]{figures/ogSalisbury}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{Without home travel:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\setlength\itemsep{-0.2em}
				\aitem Total: 38:24:18
				\aitem Travel: 01:28:22
				\aitem Waiting: 01:56:56
				\aitem Distance: 246.53km
			\end{itemize}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.7\linewidth]{figures/nurseSalisbury}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{With home travel:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\setlength\itemsep{-0.2em}
				\ditem Total: 39:14:03
				\ditem Travel: 02:01:38
				\ditem Waiting: 02:13:25
				\ditem Distance: 171.67km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame}{Comparison: Salisbury with and without carer home travel}
	\begin{figure}
		\includegraphics[width=0.5\linewidth]{figures/og_inst_Salisbury_2021-03-01_time_info_dst}%
		\includegraphics[width=0.5\linewidth]{figures/nurse_inst_Salisbury_2021-03-01_time_info_dst}
	\end{figure}
\end{frame}

% Hampshire original vs including nursesto/from home. nNurses = 21, nJobs = 68, nShifts = 24
\begin{frame} 
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\textbf{Hampshire}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.9\linewidth]{figures/ogHampshire}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{Without home travel:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\setlength\itemsep{-0.2em}
				\aitem Total: 50:02:53
				\aitem Travel: 05:30:20
				\aitem Waiting: 01:47:33
				\aitem Distance: 345.15km
			\end{itemize}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.9\linewidth]{figures/nurseHampshire}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{With home travel:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\setlength\itemsep{-0.2em}
				\ditem Total: 53:07:04
				\ditem Travel: 06:02:27
				\ditem Waiting: 04:19:37
				\ditem Distance: 363.78km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame}{Comparison: Hampshire with and without carer home travel}
	\begin{figure}
		\includegraphics[width=0.5\linewidth]{figures/og_inst_Hampshire_2021-03-01_time_info_dst}%
		\includegraphics[width=0.5\linewidth]{figures/nurse_inst_Hampshire_2021-03-01_time_info_dst}
	\end{figure}
\end{frame}

\begin{comment}
\begin{frame}{Task}
To create an efficient route and schedule for each carer such that all patients (jobs) are visited at the correct times by suitable carers.
\small
\begin{multicols}{2}
	\begin{itemize}
		\item Assign jobs to sufficiently skilled carer(s)
		\item Assign jobs to preferred carers(s)
		\item Assign carers to preferred jobs
		\item Workload balance %($\overline{B}$)
		\item Minimise waiting times %($\overline{W}$)
		\item Minimise tardiness %($\overline{Z}$)
		\item Minimise overtime %($\overline{O}$)
		\item Minimise travel time %($\overline{T}$)
		\item Minimise travel distance*
		%\item Assign jobs and carers according to preferences ($\overline{P}$)
	\end{itemize}	
\end{multicols}	
\end{frame}

@@

\begin{frame}{Queries}
\scriptsize
%\begin{multicols}{2}
	\begin{itemize}
		\item \note{Desired objective(s)}
		\item Are there skill ``levels'' for carers?
		\item Distinct job types or customised per job
		\item Jobs that \emph{cannot} start late
		\item Lunch breaks
		\item Parking availability at patient's home
		\item PPE/COVID-19 conditions
		\item Frequency of schedule formation
		\item Database/software currently used
		\item Hard and soft constraints
		\item Any additional constraints?
		\item Who will be using the application?
		\item Additional carers available?
	\end{itemize}	
%\end{multicols}
\end{frame}

@@

\begin{frame}{Comparison: Abicare vs DST}
\small
\begin{multicols}{3}	
\begin{block}{Hampshire}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 15
		\item Clients = 34
		\item Jobs = 480
	\end{itemize}
\end{block}
\begin{block}{Monmouth}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 23
		\item Clients = 47
		\item Jobs = 735
	\end{itemize}
\end{block}
\begin{block}{Aldershot}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 9
		\item Clients = 19
		\item Jobs = 184
	\end{itemize}
\end{block}
\end{multicols}	
\end{frame}
\end{comment}

\begin{comment}
\begin{frame}{Comparison: Hampshire Time and Distance}
	\begin{figure}
		\includegraphics[width=0.5\linewidth]{figures/Hampshire_time_comparison_abi}%
		\includegraphics[width=0.5\linewidth]{figures/Hampshire_dist_comparison_abi}
	\end{figure}
\end{frame}

@@

%==========================================================================================
\end{comment}
\begin{comment}
\begin{frame}{Comparison}
	\begin{figure}[T]
		\includegraphics[width=0.5\linewidth]{figures/2_Nov_20_Hampshire_time_info_abi}%
		\includegraphics[width=0.5\linewidth]{figures/2_Nov_20_Hampshire_time_info_dst}
	\end{figure}
\end{frame}
